Probabilistic Network Latency Verification

### 2023-02-08 paper/6_eval.tex
[Paper] Polish
[Paper] finished the evaluation result

\section{Evaluation}

@@

To examine the factors that affects the effectiveness of each optimization strategy, we compute some properties 
of the topology that relates to the nature of the optimization.

The effectiveness of the memoization strategy largely reflects the amount of unique paths that the functional 
verifier has explored.
The amount of unique paths (relative to the total explored paths) and the amount of reduction the memoization 
strategy gains is highly correlated, as shown by Tab. X

On the other hand, the effectiveness of the consolidation strategy is caused by more factors, such as the 
topology and the particular load-balancing scheme of the network protocol. 
As a proxy to this, we count the number of path that crosses each link, and averaged them.
As we could see from Tab. X, Uninett2010 has a measure of about 108.87, reflecting the relative ishortcoming 
of this particular strategy compared to another topology like GtsCe, which has a measure of 571.14.

% \begin{itemize}
%     \item While the amount of path in those states can explain the amount of EC reduction, to get to 
%         the amount of convolution, we also need to consider the length of each of those path
%     \item By considering the both amount of path and its length to counting the convolution, we could 
%         compare consolidation and memoization strategy to the unoptimized version
% \end{itemize}

% \begin{itemize}
%     \item Compare the amount of temporal EC to the functional (unconsolidated) EC
%     \item Corresponds to the consolidation strategy
%     \item \textbf{More than 50\% reduction}
%     \item Doesn't work equally on all topologies, depend on 
%     \begin{itemize}
%         \item How many functional EC are explored (for a given inaccuracy level)
%         \item How many possible paths a given node pair have in those ECs
%     \end{itemize}
% \end{itemize}

>>>>

\section{Evaluation} \label{eval}

@@

\subsubsection{Why is Fat Tree 10 better than Fat Tree 4?}
To analyze what affects the effectiveness of our optimization technique, we will start by explaining 
one peculiar result in our evaluation: despite having a bigger size, the temporal verification runtime 
of fat tree with $k = 10$ is faster than $k = 4$.

This is due to the fact that the shortest path in $k = 10$ is a lot more diverse than that of $k = 4$.
In a 3-tier Fat Tree topology, an edge node could reach another pod's edge node in at least 4 hops.
The amount of this shortest path is $(k/2)^2$, which is the same as the number of core node.

We could see from Table \ref{tab:analysis} that when $k \geq 10$, the amount of unique path explored by the 
functional verifier is exactly the same as the number of core node. 
Combined with the fact that the average amount of convolution per path is 7 (which suggests that the path 
length is 4), means that the functional verifier only produces equivalence classes that consisted of only 
different combination of these shortest paths.

When $k < 10$ however, the functional verifier also needs to produce equivalence classes that results 
in a longer convergent paths in order to reach the same accuracy level.
in Fat Tree, this is usually marked by a visit to another aggregation node in another pod. 
We could see from Table \ref{tab:analysis} that when $k < 10$, the amount of of convolution per path is more 
than 7 (which suggests that a path longer than 4 hops exist).

\subsubsection{Generalization}
From the insight of this particular result, we could draw two properties in a general network that could 
determine the runtime of our verifier.

The first one is the \textbf{amount of possible paths}.
If the amount of possible paths between a src-dst pair in a given topology is small, then the functional 
verification step would produce fewer equivalence classes and end early.
While most of our evaluated topology had a lot of possible paths, one exception to this is LatNet, which 
only have 3 possible paths.

The second is whether the src-dst pair in a given topology would \textbf{produce paths that are "symmetric"}.
By symmetric, we mean that the routing and load balancing method produce a lot of identical equivalence class 
and / or equivalence class that share the same path.
As our explanation about Fat Tree 10 suggests, larger Fat Tree has a lot of path with the same length.
This would result in a lot of symmetrical equivalence classes under ECMP.
Our optimization techniques could identify this symmetry and reduce the amount of convolution in the temporal 
verification step.

%TODO: path enumeration?

### 2023-02-08 paper/main.tex
[Paper] Completed section 2
[Paper] Polish
[Paper] finished the evaluation result

\begin{document}
\begin{abstract}
    To combat configuration errors that a given network might have, network verifiers have emerged as 
    one of the promising solution. 
    State-of-the-art network verifiers mainly focused on evaluating qualitative properties under 
    various scenarios of network failures, such as reachability under loop detection.

@@

    In this work, we introduce a verifier framework, Tempus, that can answer the probability of 
    a given temporal property being true given latency distributions of individual links and 
    nodes in the network.

    Our evaluation shows that \tool can verify bounded reachability property -- the probability
    that the average delay of packets traversing from a source to destination node is below $T$
    time unit -- by only adding a fraction of the state exploration overhead introduced by the 
    qualitative verifier it's built upon.
\end{abstract}

@@

\input{5_eval.tex}

\input{6_related.tex}

\input{7_future.tex}

\section{Conclusion}
\begin{itemize}
    \item Tempus is a scalable latency SLA verifier. It could probabilistically verify in the order of minutes
    \item Consolidation and memoization is an effective optimization strategy, although the exact magnitude of 
        its effectiveness will depend on the network topology, specifically on the amount of paths and their 
        length.
\end{itemize}

>>>>

\begin{document}
\begin{abstract}
    To combat configuration errors that a given network might have, network verifiers have emerged as 
    one of the promising solution. 
    State-of-the-art network verifiers mainly focused on evaluating qualitative properties under 
    various scenarios of network failures, such as reachability and loop detection.

@@

    In this work, we introduce a verification framework, \tool, that can answer the probability of 
    a given temporal property being true given latency distributions of individual links and 
    nodes in the network. 
    We use the convolution operation on these probability distributions to calculate the end-to-end 
    path latency distribution, and answer property by analyzing the statistical property of this 
    resulting distribution.
    We also introduce two effective optimization techniques to exploit the symmetry in the verification 
    process to reduce the amount of convolution operation needed.

    Our evaluation shows that \tool can verify temporal property 4 orders of magnitude faster on average than 
    our baseline, which is devoid of all optimization.
    We also identify that highly symmetrical topology, like Fat Tree, benefits from our optimization the most 
    and can cut the amount of convolution up to 6 orders of magnitude.
\end{abstract}

@@

\input{5_opt.tex}

\input{6_eval.tex}

\input{8_future.tex}

\input{7_related.tex}

\section{Conclusion} \label{sec:conc}
\begin{itemize}
    \item Tempus is a scalable latency SLA verifier. It could probabilistically verify in the order of minutes
    \item Consolidation and memoization is an effective optimization strategy, although the exact magnitude of 
        its effectiveness will depend on the network topology, specifically on the amount of paths and their 
        length.
\end{itemize}
